Assistant Tools and Accessibility Features for Blind People Playing Visual-Centric Digital Games

### 2024-02-17 Paper/paper.tex
minor changes

    In summary, it can be said that the game industry already takes into account the most important accessibility features, yet most modern visually-centric digital games are still a major challenge for blind players.
    In the following section we will delve deeper into some of the listed features above, their problems and possible solutions, as well as how to improve the overall experience of blind people.

	\section{Related Work}
	As digital games continuous to evolve making them more complex to play, accessibility becomes increasingly more important.
	This section provides a deeper insight in related works that contributed to the understanding of how important accessibility in visual-centric digital games is.

@@

	The paper highlighted the limitation of the study such as the small sample size and the need for further research to validate their findings.
	Nevertheless, this paper gives important insight of what can be achieved with echolocation to help blind players.

>>>>

    In summary, it can be said that the game industry already takes into account the most important accessibility features, yet most modern visual-centric digital games are still a major challenge for blind players.
    In the following section we will delve deeper into some of the listed features above, their problems and possible solutions, as well as how to improve the overall experience of blind people.

	\section{Related Work}
	As digital games continuous to evolve making them more complex to play, accessibility becomes increasingly more important.
	This section provides a deeper insight into related work that has contributed to the understanding of the importance of accessibility in visual-centric digital games.

@@

	The paper highlighted the limitation of the study such as the small sample size and the need for further research to validate their findings.
	Nevertheless, this work provides an important insight into the possibilities of using echolocation to help blind players.
